\documentclass{resume}
\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\usepackage{fontawesome}
\usepackage{hyperref}

\name{Aqib Shah}
\address{+92 305 7068821 | csaqibshah@gmail.com}
\address{
    \href{https://github.com/aqibcs}{\faIcon{github}} { }
    \href{https://www.linkedin.com/in/aqibcs/}{\faIcon{linkedin}} { }
}
\address{Lahore, Punjab, Pakistan}

\begin{document}

\begin{rSection}{Summary}
    I'm an experienced backend developer who's good at using Golang and Python. I've helped improve processes and come up with new ideas. I work well in teams, learn new things quickly, and can make scalable solutions.
\end{rSection}

\begin{rSection}{Skills \& Interests}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        Languages         & Golang, Python                         \\
        Frameworks        & go-chi, Echo, Flask, Django \\
        Relational Models & GORM                              \\
        Databases         & PostgreSQL, MySQL, Neo4j         \\
        DevOps            & Docker		         \\
        Version Control   & Git, Github		         \\
    \end{tabular}
\end{rSection}

\begin{rSection}{Work Experience}
    \begin{rSubsection}{Datum Brain}{September 2023 - February 2024}{Internship}{Lahore, Pakistan}
        \item As a dedicated \textbf{Backend Developer} at \textbf{Datum Brain} with a focus on \textbf{Golang} and \textbf{Python}, I have played a crucial role in advancing the technological landscape of the company.
        \item Led compliance-focused data scraping for a \textbf{microfinance app}, optimizing processes and reducing processing time by \textbf{20\%}.
        \item Developed \textbf{OCR} for document verification, processing 5,000+ documents monthly with a \textbf{15\%} accuracy improvement.
        \item Implemented \textbf{machine-readable text extraction for passports}, automating processes and achieving \textbf{98\%} accuracy.
        \item Refactored \textbf{ERP} Invoice module, changing the framework to \textbf{Echo}, resulting in a \textbf{40\%} response time improvement and \textbf{25\%} fewer errors.
    \end{rSubsection}
\end{rSection}

\begin{rSection}{EDUCATION}
    {\bf Diploma in Information Technology} \hfill {2020 - 2021}
    \\
        Government Technical & Vocational Centre Umerzai, Charsadda, KPK
    \\
    \\
    {\bf Bachelor of Business \& Information Technology (BBIT)} \hfill {2024 - Present}
    \\
    Virtual University of Pakistan
    \\
\end{rSection}

\begin{rSection}{Problem Solving}
    \begin{itemize}
        \item Golang, Python - LeetCode \href{https://leetcode.com/csaqibshah/}{\faIcon{code}}
    \end{itemize}
\end{rSection}

\begin{rSection}{Other Information}
    \item Consistently demonstrated problem-solving skills, effective communication, and the ability to work collaboratively in a team.
    \item Adept at adapting to new technologies and frameworks, as evidenced by successful projects during the internship.
\end{rSection}

\end{document}
